An assessment of photometric redshift PDF performance in the context of LSST

### 2018-10-10 paper/tex/results.tex
fix merge cruft in results.tex
remove seaborn from Fig 4

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{fig/NZsumplot_12codes_scottsrule.jpg}
\caption{The stacked $p(z)$ produced by each photo-$z$ code ($\hat{N}(z)$, red) compared to the spectroscopic redshift distribution ($N'(z)$, blue).  Varying levels of small-scale structure are seen in the codes.  Both $\hat{N}(z)$ and $N'(z)$ are smoothed using a single bandwidth chosen via Scott's rule for all codes.} \label{fig:nz}
%\aim{Arguably this could also be clarified by showing the true $n'(z)$ once and then differences from it for each cod's stacked estimator\dots}\scc{what if we plot the difference between true and stacked rather than soverposing the two lines? Sam please do not hate me.}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{fig/NZsumplot_12codes_scottsrule.jpg}
\caption{The stacked $p(z)$ produced by each photo-$z$ code ($\hat{N}(z)$, red) compared to the spectroscopic redshift distribution ($N'(z)$, blue).  Varying levels of agreement are seen in the codes.  Both $\hat{N}(z)$ and $N'(z)$ in all codes are smoothed using a single bandwidth chosen via Scott's rule.} \label{fig:nz}
%\aim{Arguably this could also be clarified by showing the true $n'(z)$ once and then differences from it for each cod's stacked estimator\dots}\scc{what if we plot the difference between true and stacked rather than soverposing the two lines? Sam please do not hate me.}
\end{figure*}
